Temperature Measurements in Optical Tweezer Experiments

### 2017-01-16 doc/draft1.tex
updates

\subsection{Barostat}
The barostat, as described in the previous section, keeps the system from overheating. The algorithm is applied at the same time as the eHEX algorithm
which leads to the fact, that the system has time to heat up, until the particles reach the nano crystal. This can be seen in the temperature
development in fig.~\ref{fig:baro1}.
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.4]{images/ehex_te.pdf}
        \caption{}
        \label{fig:baro1}
    \end{center}
\end{figure}

>>>>

\subsection{Barostat}
The barostat, as described previously, keeps the system from overheating. The barostat algorithm is applied at the same time as the eHEX algorithm,
after the velocity Verlet has equilibrated the system. This means that the system is beginning to heat up, until the particles reach the crystal.
Because of this, the temperature of the system rises, until it reaches a steady value again. This behaviour can be seen in fig.~\ref{fig:baro1}.
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.4]{images/ehex_te.pdf}
        \caption{}
        \label{fig:baro1}
    \end{center}
\end{figure}
